From Education to Entrepreneurship

### 2014-12-07 index.Rmd
Updated link to reflect reorganized repository

# Import csv of df with imputed figures (created in Index_sources/Amelia_source)
CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)

>>>>

# Import csv of df with imputed figures (created in Index_sources/Amelia_source)
CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/GEMData/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)
